Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-21 prob.tex
prob.tex Fix some typos...

Notice that $\pmeas(\emptyset)=0$ and equation~(\ref{eq:ClassicalReal-valuedProbability-Complement})
can be induced by other conditions. They are listed in here so that
we can compare definition~\ref{def:ClassicalProbabilitySpace}, lemma~\ref{lem:classicalProbabilityMeasure},
definition~\ref{def:QuantumProbabilitySpace}, and definition~\ref{def:QuantumInterval-valuedProbability}
easily. We will compare these lemma and definitions when we try to
formulate quantum interval-valued probability measures later.

@@

In the previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although each event is assumed to have
a probability, the exact value of $\pmeas(E)$ may not be known. If
we want to know its value, we can run $N$ independent trials. Let
$x_{i}=1$ or $0$ denote whether the event~$E$ occurs in the $i$-th
trial or not, respectively, then $\pmeas(E)$ could be approximated
to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\sum_{i=1}^{N}x_{i}$
with the probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sum_{i=1}^{N}x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story might go to section~\ref{sec:DQT}.
The problem of this approach is that Because we don't really use $\mathbb{C}$
in example~\ref{ex:three-dimensional-three-value}, I could expect
example~\ref{ex:three-dimensional-three-value} is highly likely
to serve as an counterexample for discrete interval-valued Gleason's
theorem...

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do thing correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach might go to section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. More precisely, we might need to verify tensor product
and quantum teleportation works in this model...}

@@

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some strange
conditions to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.

>>>>

Notice that $\pmeas(\emptyset)=0$ and equation~(\ref{eq:ClassicalReal-valuedProbability-Complement})
can be induced by other conditions. They are listed in here so that
we can compare definition~\ref{def:ClassicalProbabilitySpace}, lemma~\ref{lem:classicalProbabilityMeasure},
definition~\ref{def:QuantumProbabilitySpace}, and definition~\ref{def:QuantumInterval-valuedProbability}
easily. We will compare these lemma and definitions when we formulate
quantum interval-valued probability measures later.

@@

In the previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although each event is assumed to have
a probability, the exact value of $\pmeas(E)$ may not be known. If
we want to know its value, we can run $N$ independent trials. Let
$x_{i}=1$ or $0$ denote whether the event~$E$ occurs in the $i$-th
trial or not, respectively, then $\pmeas(E)$ could be approximated
to given accuracy~$\epsilon>0$ by the relative frequency~$\frac{1}{N}\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}x_{i}$
with the probability converging to one as $N$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{N\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{N}\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story might go to section~\ref{sec:DQT}.
The problem of this approach is that Because we don't really use $\mathbb{C}$
in example~\ref{ex:three-dimensional-three-value}, I could expect
example~\ref{ex:three-dimensional-three-value} is likely to serve
as an counterexample for discrete interval-valued Gleason's theorem...

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach might go to section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. More precisely, we might need to verify tensor product
and quantum teleportation works in this model...}

@@

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some extra-conditions
(like \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
is too small...) to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.
